---
title: 'Advent Of Code: 2021-24'
author: Leo Carlsson
date: "`r Sys.Date()`"
output: html_document
---

```{r setup}
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(glue)
  
  knitr::opts_chunk$set(echo = TRUE)
})

options(scipen = 9999999)
options(dplyr.summarise.inform = FALSE)
```

--- Data ---

```{r eval = FALSE}
aoc.elf::aoc_get(day = 24, year = 2021)
```

```{r}
input <- readLines(here::here("2021/day-24-input.txt"))[1:18] 

tibble(x = input) |> 
  separate(x, sep = " ", into = c("operation", "value1", "value2"))
input
```




Write a short program that prints each number from 1 to 100 on a new line. 

For each multiple of 3, print "Fizz" instead of the number. 

For each multiple of 5, print "Buzz" instead of the number. 

For numbers which are multiples of both 3 and 5, print "FizzBuzz" instead of the number.

```{r}
FizzBuzz <- function(input) {
  if (input %% 3 == 0  & input %% 5 == 0) return("FizzBuzz")
  else if (input %% 3 == 0 ) return("Fizz")
  else if (input %% 5 == 0) return("Buzz")
  else return(as.character(input))
}

lapply(1:100, FizzBuzz)
```


```{r}
FizzBuzz <- function(input) {
  if (input %% 3 == 0  & input %% 5 == 0) print("FizzBuzz")
  else if (input %% 3 == 0 ) print("Fizz")
  else if (input %% 5 == 0) print("Buzz")
  else print(as.character(input))
}

sapply(1:100, FizzBuzz)

for (i in 1:100) {
  FizzBuzz(i)
}
```

TwoSum
Given an array of integers nums and an integer target, return indices of the two numbers such that they add up to target.

You may assume that each input would have exactly one solution, and you may not use the same element twice.

You can return the answer in any order.

Example 1:
Input: nums = [2,7,11,15], target = 9
Output: [0,1]
Output: Because nums[0] + nums[1] == 9, we return [0, 1].
Example 2:

Input: nums = [3,2,4], target = 6
Output: [1,2]


```{r}
twoSum <- function(numbers, target) {
  for (i in seq_along(numbers)) {
    for (j in seq_along(numbers)) {
      test <- numbers[i] + numbers[j] == target
      if (test) {
        return(c(i, j))
      }
    }
  }
}
nums <- c(2,7,11,15)
target <- 9

twoSum(nums, target)
```

Gives correct!  But, it does not handle them two same numbers. ie, 
```{r}
nums <- c(3,2,4)
target <- 6

twoSum(nums, target)
```

Change so we test if 

```{r}
twoSum <- function(numbers, target) {
  for (i in seq_along(numbers)) {
    for (j in seq_along(numbers)) {
      test <- numbers[i] + numbers[j] == target & i != j
      if (test) {
        return(c(i, j))
      }
    }
  }
}

twoSum(nums, target)
```

```{r}
map_twosum <- function(numbers, target) {
  map_int(seq_along(numbers), 
          ~print(numbers[.x])
  )
}

map_twosum(nums, target)
```


```{r}
twosum <- function(.x, nums = numbers, target = target) {
    comp <- target - nums[.x] 
    if (comp %in% nums) {
      first <- .x
      second <- which(nums %in% comp)
      return(c(first, second))
    } else return(NULL)
  }

map_twosum <- function(numbers, target) {
  map(seq_along(numbers), ~twosum(.x, nums = numbers, target = target)
  )
}

map_twosum(nums, target)

```


```{r}
nums = c(3,3)
target = 6
twoSum(nums, target)
```

Product of array execpt self

Input: nums = [1,2,3,4]
Output: [24,12,8,6]
```{r}
ProductArray <- function(nums) {
  index <- seq_along(nums)
  
  map(index, ~prod(nums[-.x])) |> unlist()
}

nums <-  c(1,2,3,4)
expexted_output <- c(24,12,8,6)
output <- ProductArray(nums)
all(output == expexted_output)

nums <- c(-1,1,0,-3,3)
expexted_output <- c(0,0,9,0,0)
output <- ProductArray(nums)
all(output == expexted_output)
```


```{r}
nums <- c(1,2,3,4, 1,2,3,4,1,2,3,4, 1,2,3,4,1,2,3,4, 1,2,3,4,1,2,3,4, 1,2,3,4, 1,2,3,4, 1,2,3,4,1,2,3,4, 1,2,3,4,1,2,3,4, 1,2,3,4,1,2,3,4, 1,2,3,4)
```


```{r}
tictoc::tic()
output <- ProductArray(nums)
tictoc::toc()
```

```{r}
tictoc::tic()
output <- c()
for (i in seq_along(nums)) {
  output <- c(output, prod(nums[-i]))
}
tictoc::toc()
```

